Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-01 paper/paper.tex
Add more system overview text

@@

We currently deal with a read-only workload where the distribution of data is known by all nodes.
Each node is able to calculate the fraction of query results it will return.
A node can signal the expected fraction of the results for a query it will return by setting bits within the packet header.
When a new flow is issued for query processing, the controller can inspect these bits and assign an appropriate priority to each flow.

>>>>

Our system uses OpenFlow~\cite{McKeown2008} enabled switches to allow centralized network control.
We currently pass all queries through our SDN controller which is running on the POX~\cite{Gude2008} platform.

@@

We currently deal with a read-only workload where the distribution of data is known by all nodes.
Each node is able to calculate the fraction of query results it will return.
A node can signal the expected fraction of the results for a query it will return by setting bits within the packet header.
When a new flow is issued for query processing, the controller can inspect these bits and assign an appropriate priority to each flow.
The controller is similar to a simple L2 learning switch.
However, we configure several queues for each switch port which allow us to provide bandwidth reservations to support variation in expected traffic volume.

We also change the flow table rules we install to match on the type of service (ToS) bits in the IP header.
Two of these eight bits are often used for explicit congestion notification (ECN).
We avoid these bits to allow ECN to operate uninhibited.
The remaining six bits are the differentiated services code point (DSCP) which are used to provide varying QoS guarantees for different flows.
We assume that the portion of the network our system is operating on is not carrying other traffic so we are free to set these bits as we choose.
To interconnect with other networks which may assign different meaning to these bits, we can simply zero these bits for any traffic passing through ingress/egress switches.
